Viability of FTIR on fossil pollen

### 2020-03-03 manuscript.Rmd
added references for Tinner samples

Tinner meso-mediterranean:
Quercus sections Quercus, Cerris and Ilex

Tinner thermo-mediterranean:
Quercus sections Quercus, Cerris and Ilex

>>>>

Tinner meso-mediterranean:
[@bisculmHoloceneVegetationFire2012; @vanniereClimateHumandrivenFire2008]
Quercus sections Quercus, Cerris and Ilex

Tinner sub-mediterranean:
[@zoller19601960]
Quercus sections Quercus, Cerris and Ilex
